Maximising the leverage of existing knowledge could reduce research waste in applied ecology and conservation

### 2019-11-27 Manuscript/MS.Rmd
27.11.2019

 }
      [1]: 'Questions relevant to stakeholders'
      [2]: 'Appropriate design & methods'
      [3]: 'Accessible full publication'
      [4]: 'Unbiased reporting'
      [5]: 'Wasteful research'
      [6]: 'Evidence synthesis'
      [7]: 'Utilisable research' 
      [8]: 'Previous knowledge not accounted for'
      [9]: 'Poor design; \\nquestionable research practices'
      [10]: 'Publications not available to practitioners \\n& decision makers'
      [11]: 'Lack of transparency'
  ", height=1000)

@@

  #geom_text(aes(label=as.factor(Year)),hjust=0.5, vjust=0)+
  geom_hline(yintercept = 2, colour="red",linetype="dotted", size=1.6)+
  geom_hline(yintercept = -2, colour="red",linetype="dotted", size=1.6)+
  theme_classic() +
  theme(axis.line = element_line(size = 1.6, color = rgb(0,0,0,max=255)))+
  theme(legend.position = "none")+
  theme(text=element_text(size=16,  family="serif"))
```

>>>>

 }
      [1]: 'Questions relevant to stakeholders'
      [2]: 'Appropriate design & methods'
      [3]: 'Unbiased reporting'
      [4]: 'Accessible full publication'
      [5]: 'Wasteful research'
      [6]: 'Evidence synthesis'
      [7]: 'Utilisable research' 
      [8]: 'Previous knowledge not accounted for'
      [9]: 'Poor design; \\nquestionable research practices'
      [10]: 'Lack of transparency'
      [11]: 'Publications not available to practitioners \\n& decision makers'
  ", height=1000)

@@

  #geom_text(aes(label=as.factor(Year)),hjust=0.5, vjust=0)+
  geom_hline(yintercept = 2, colour="red",linetype="dotted", size=1.6)+
  geom_hline(yintercept = -2, colour="red",linetype="dotted", size=1.6)+
  theme_classic() +
  theme(axis.line = element_line(size = 1.6, color = rgb(0,0,0,max=255)))+
  theme(legend.position = "none")+
  theme(text=element_text(size=16,  family="serif"))
#dev.off()
```
